Identifying regime transitions for water governance at a basin scale

### 2023-05-10 paper/main/03_results.tex
feat(paper): :sparkles: 回答审稿人关于水库运输的问题
1. 运输是手段，2. 不增加复杂性，3. 讨论增加了一张图

IWGI在“应力”方面包含储层存储信息。输水能力是衡量水治理/水社会复原力的重要指标。

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Environmental context, social transformation, and policies played roles in all three periods.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
Ensuing the P2, the number of new reservoirs decreased significantly and significantly increased basin policies rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.

>>>>

% 最后，环境背景、社会转型和水治理政策在这三个时期都发挥了作用。
Environmental context, social transformation, and policies played roles in all three periods.
We calculated the ratios of regional and basinal water use for each reservoir (R/B ratio) (Figure~\ref{fig:Causes}C), with a higher ratio representing a potential role in water supply rather than basinal regulations.
Under the banner of ``conquering nature'' most of the reservoirs were built in regions with high water demands during the P1 (R/B ratios were significantly higher ($p<0.01$, see Figure~\ref{fig:Causes}C)).
Ensuing the P2, the number of new reservoirs decreased but boosted their role in water regulating and management (more red circles in Figure~\ref{fig:Causes}~C, and larger water conveyance variability in Supplementary Materials Figure~S7).  % todo 检查图引用
Basin policies significantly increased, rigorously controlled the allocation of water (Figure~\ref{fig:Causes}D, $p<0.01$ and \textit{Supporting Information} Figure~S2).
During the P3, authorities proposed more national-level water governance policies under the guidance of the national strategy ``environmental regulation'' (Figure~\ref{fig:Causes}D).
The regime shift from P1 to P2 is in line with the increasing water supply and demands; while driven by regulatory policies and efficiency enhancement under stable water stress from P2 to P3.
